Lineage Analysis of CRISPR and shRNA Screens

### 2018-10-08 lineages_18Q3.Rmd
updated Fig 1C plots

crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
  guides(color = FALSE) +
  geom_text(data = label_text, mapping = aes(x = 1.5, y = 4.5, label = p.signif.adj)) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.25, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_filt_plot_faceted
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 4, units = "in")

>>>>

crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  coord_cartesian(ylim = c(-3, 5)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
  guides(color = FALSE) +
  geom_text(data = label_text, mapping = aes(x = 1.5, y = 5, label = p.signif.adj)) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_filt_plot_faceted
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 4, units = "in")
